\chapter{400 Boys}
\chapterauthor{Marc Laidlaw}

The cyberpunk writers are known for bizarre concepts and a general allegiance to the strange. Marc Laidlaw stands out even in this company. His work is marked by odd leaping juxtapositions, unexpected angles of vision, and a black humor that shades into the ultraviolet. He draws inspiration from a slew of contemporary influences, with a special fondness for all that is mysterious, intuitive, and outré.

The following story demonstrates Laidlaw's inspired fusion of elements, blending features of apocalyptic myth with the modern legendry of urban street gangs. “400 Boys” is a genuinely weird, headlong mélange that is much more easily enjoyed than described.

Marc Laidlaw lives in San Francisco. His latest novel is Dad's Nuke.

\hrulefill

``Sacrifice us!''

—The Popol Vuh
 
\firstletter{W}e sit and feel Fun City die. Two stories above our basement, at street level, something big is stomping apartment pyramids flat. We can feel the lives blinking out like smashed bulbs; you don't need second sight to see through other eyes at a time like this. I get flashes of fear and sudden pain, but none last long. The paperback drops from my hands, and I blow my candle out.

We are the Brothers, a team of twelve. There were twenty-two yesterday, but not everyone made it to the basement in time. Our slicker, Slash, is on a crate loading and reloading his gun with its one and only silver bullet. Crybaby Jaguar is kneeling in the corner on his old blanket, sobbing like a maniac; for once he has a good reason. My best Brother, Jade, keeps spinning the cylinders of the holotube in search of stations, but all he gets is static that sounds like screaming turned inside out. It's a lot like the screaming in our minds, which won't fade except as it gets squelched voice by voice.

Slash goes, “Jade, turn that thing off or I'll short-cirk it.”

He is our leader, our slicker. His lips are gray, his mouth too wide where a Soooooot scalpel opened his cheeks. He has a lisp.

Jade shrugs and shuts down the tube, but the sounds we hear instead are no better. Faraway pounding footsteps, shouts from the sky, even monster laughter. It seems to be passing away from us, deeper into Fun City.
“They'll be gone in no time,” Jade goes.

“You think you know everything,” goes Vave O'Claw, dissecting an alarm clock with one chrome finger the way some kids pick their noses. “You don't even know what they are—”

“I saw ‘em,” goes Jade. “Croak and I. Right, Croak?”

I nod without a sound. There's no tongue in my mouth. I only croaked after my free fix-up, which I got for mouthing badsense to a Controller cognibot when I was twelve.

Jade and I went out last night and climbed an empty pyramid to see what we could see. Past Riverrun Boulevard the world was burning bright, and I had to look away. Jade kept staring and said he saw wild giants running with the glow. Then I heard a thousand guitar strings snapping, and Jade said the giants had ripped up Big Bridge by the roots and thrown it at the moon. I looked up and saw a black arch spinning end over end, cables twanging as it flipped up and up through shredded smoke and never fell back—or not while we waited, which was not long.

“Whatever it is could be here for good,” goes Slash, twisting his mouth in the middle as he grins. “Might never leave.”

Crybaby stops snorting long enough to say, “Nuh-never?”

“Why should they? Looks like they came a long way to get to Fun City, doesn't it? Maybe we have a whole new team on our hands, Brothers.”

“Just what we need,” goes Jade. “Don't ask me to smash with ‘em, though. My blade's not big enough. If the Controllers couldn't keep ‘em from crashing through, what could we do?”

Slash cocks his head. “Jade, dear Brother, listen close. If I ask you to smash, you smash. If I ask you to jump from a hive, you jump. Or find another team. You know I only ask these things to keep your life interesting.”
“Interesting enough,” my best Brother grumbles.

“Hey!” goes Crybaby. He's bigger and older than any of us but doesn't have the brains of a ten-year-old. “Listen!”

We listen.

“Don't hear nothin',” goes Skag.

“Yeah! Nuh-nuthin'. They made away.”

He spoke too soon. Next thing we know there is thunder in the wall, the concrete crawls underfoot, and the ceiling rains. I dive under a table with Jade.

The thunder fades to a whisper. Afterward there is real silence.

“You okay, Croak?” Jade goes. I nod and look into the basement for the other Brothers. I can tell by the team spirit in the room that no one is hurt.

In the next instant we let out a twelve-part gasp.

There's natural light in the basement. Where from?

Looking out from under the table, I catch a parting shot of the moon two stories and more above us. The last shock had split the old tenement hive open to the sky. Floors and ceilings layer the sides of a fissure; water pipes cross in the air like metal webs; the floppy head of a mattress spills foam on us.

The moon vanishes into boiling black smoke. It is the same smoke we saw washing over the city yesterday, when the stars were sputtering like flares around a traffic wreck. Lady Death's perfume comes creeping down with it.
Slash straddles the crack that runs through the center of the room.

He tucks his gun into his pocket. The silver of its only bullet was mixed with some of Slash's blood. He saves it for the Sooooot who gave him his grin, a certain slicker named HiLo.

“Okay, team,” he goes. “Let's get out of here pronto.”

Vave and Jade rip away the boards from the door. The basement was rigged for security, to keep us safe when things got bad in Fun City. Vave shielded the walls with baffles so when Controller cognibots came scanning for hideaways, they picked up plumbing and an empty room. Never a scoop of us.

Beyond the door the stairs tilt up at a crazy slant; it's nothing we cannot manage. I look back at the basement as we head up, because I had been getting to think of it as home.

We were there when the Controllers came looking for war recruits. They thought we were just the right age.
“Come out, come out, wherever in free!” they yelled. When they came hunting, we did our trick and disappeared.
That was in the last of the calendar days, when everyone was yelling: “Hey! This is it! World War Last!”

What they told us about the war could be squeezed into Vave's pinky tip, which he had hollowed out for explosive darts. They still wanted us to fight in it. The deal was, we would get a free trip to the moon for training at Base English, then we would zip back to Earth charged up and ready to go-go-go. The SinoSovs were hatching wars like eggs, one after another, down south. The place got so hot that we could see the skies that way glowing white some nights, then yellow in the day.

Federal Control had sealed our continental city tight in a see-through blister: Nothing but air and light got in or out without a password. Vave was sure when he saw the yellow glow that the SinoSovs had launched something fierce against the invisible curtain, something that was strong enough to get through.

Quiet as queegs we creep to the Strip. Our bloc covers Fifty-sixth to Eighty-eighth between Westland and Chico. The streetlights are busted like every window in all the buildings and the crashed cars. Garbage and bodies are spilled all over.

“Aw, skud,” goes Vave.

Crybaby starts bawling.

“Keep looking, Croak,” goes Slash to me. “Get it all.”

I want to look away, but I have to store this for later. I almost cry because my ma and my real brother are dead. I put that away and get it all down. Slash lets me keep track of the Brothers.

At the Federal Pylon, where they control the programmable parts and people of Fun City, Mister Fixer snipped my tongue and started on the other end.

He did not live to finish the job. A team brigade of Quazis and Moofs, led by my Brothers, sprang me free.

That takes teamwork. I know the Controllers said otherwise, said that we were smash-crazy subverts like the Anarcanes, with no pledge to Fun City. But if you ever listened to them, salt your ears. Teams never smashed unless they had to. When life pinched in Fun City, there was nowhere to jump but sideways into the next bloc. Enter with no invitation and … things worked out.

I catch a shine of silver down the Strip. A cognibot is stalled with scanners down, no use to the shave-heads who sit in the Pylon and watch the streets.

I point it out, thinking there can't be many shave-heads left.

“No more law,” goes Jade.

“Nothing in our way,” goes Slash.

We start down the Strip. On our way past the cog, Vave stops to unbolt the laser nipples on its turret. Hooked to battery packs, they will make slick snappers.

We grab flashlights from busted monster marts. For a while we look into the ruins, but that gets nasty fast. We stick to finding our way through the fallen mountains that used to be pyramids and block-long hives. It takes a long time.

There is fresh paint on the walls that still stand, dripping red-black like it might never dry. The stench of fresh death blows at us from center city.

Another alley cat pissed our bloc.

I wonder about survivors. When we send our minds out into the ruins, we don't feel a thing. There were never many people here when times were good. Most of the hives emptied out in the fever years, when the oldies died and the kiddy kids, untouched by disease, got closer together and learned to share their power.

It keeps getting darker, hotter; the smell gets worse. Bodies staring from windows make me glad I never looked for Ma or my brother. We gather canned food, keeping ultraquiet. The Strip has never seen such a dead night. Teams were always roving, smashing, throwing clean-fun free-for-alls. Now there's only us.

We cross through bloc after bloc: Bennies, Silks, Quazis, Mannies, and Angels. No one. If any teams are alive they are in hideaways unknown; if they hid out overground they are as dead as the rest.

We wait for the telltale psychic tug—like a whisper in the pit of your belly—that another team gives. There is nothing but death in the night.

“Rest tight, teams,” Jade goes.

“Wait,” goes Slash.

We stop at two hundred sixty-fifth in the Snubnose bloc. Looking down the Strip, I see someone sitting high on a heap of ruined cement. He shakes his head and puts up his hands.

“Well, well,” goes Slash.

The doob starts down the heap. He is so weak he tumbles and avalanches the rest of the way to the street. We surround him, and he looks up into the black zero of Slash's gun.

“Hiya, HiLo,” Slash goes. He has on a grin he must have saved with the silver bullet. It runs all the way back to his ears. “How's Soooooots?”

HiLo doesn't look so slick. His red-and-black lightning-bolt suit is shredded and stained, the collar torn off for a bandage around one wrist. The left lens of his dark owlrims is shattered, and his buzzcut is scraped to nothing.

HiLo doesn't say a word. He stares up into the gun and waits for the trigger to snap, the last little sound he will ever hear. We are waiting, too.

There's one big tear dripping from the shattered lens, washing HiLo's grimy cheek. Slash laughs. Then he lowers the gun and says, “Not tonight.”

HiLo does not even twitch.

Down the Strip, a gas main blows up and paints us all in orange light.

We all start laughing. It's funny, I guess. HiLo's smile is silent.

Slash jerks HiLo to his feet. “I got other stuff under my skin, slicker. You look like runover skud. Where's your team?”

HiLo looks at the ground and shakes his head slowly.

``Slicker,” he goes, “we got flattened. No other way to put it.” A stream of tears follows the first; he clears them away. “There's no Soooooots left.”

``There's you,” goes Slash, putting a hand on HiLo's shoulder.

``Can't be a slicker without a team.”

``Sure you can. What happened?”

HiLo looks down the street. “New team took our bloc,” he goes. “They're giants, Slash—I know it sounds crazy.”

``No,” goes Jade, “I seen ‘em.”

HiLo goes, “We heard them coming, but if we had seen them I would never have told the Soooooots to stand tight. Thought there was a chance we could hold our own, but we got smeared. “They threw us. Some of my buds flew higher than the Pylon. These boys… incredible boys. Now 400th is full of them. They glow and shiver like the lights when you get clubbed and fade out.”

Vave goes, “Sounds like chiller-dillers.”

``If I thought they were only boys I wouldn't be scared, Brother,” goes HiLo. “But there's more to them. We tried to psych them out, and it almost worked. They're made out of that kind of stuff: It looks real, and it will cut you up, but when you go at it with your mind it buzzes away like bees. There weren't enough of us to do much. And we weren't ready for them. I only got away because NimbleJax knocked me cold and stuffed me under a transport.
“When I got up it was over. I followed the Strip. Thought some teams might be roving, but there's nobody. Could be in hideaways. I was afraid to check. Most teams would squelch me before I said word one.”

``It's hard alone, different with a team behind you,'' goes Slash. ``How many hideaways do you know?''

“Maybe six. Had a line on JipJaps, but not for sure. I know where to find Zips, Kingpins, Gerlz, Myrmies, Sledges. We could get to the Galrog bloc fast through the subtunnels.”
Slash turns to me. “What have we got?”
I pull out the beat-up list and hand it to Jade, who reads it. “JipJaps, Sledges, Drummers, A-V-Marias, Chix, Chogs, Dannies. If any of them are still alive, they would know others.”

``True,'' goes Slash.

Jade nudges me. ``Wonder if this new team has got a name.''

He knows I like spelling things out. I grin and take back the list, pull out a pencil, and put down 400 BOYS.
“Cause they took 400th,” Jade goes. I nod, but that is not all. Somewhere I think I read about Boys knocking down the world, torturing grannies. It seems like something these Boys would do.

Down the street the moon comes up through smoke, making it the color of rust. Big chunks are missing.
``We'll smash em,'' goes Vave.

The sight of the moon makes us sad and scared at the same time, I remember how it had been perfect and round as a pearl on jewelrymart velvet, beautiful and brighter than streetlights even when the worst smogs dyed it brown. Even that brown was better than this chipped-away bloody red. Looks like it was used for target practice. Maybe those Boys tossed the Bridge at Base English.

“Our bloc is gone,” goes HiLo. “I want those Boys. It'll be those doobs or me.”

“We're with you,” goes Slash. “Let's move fast. Cut into pairs, Brothers. We're gonna hit some hideaways. Jade, Croak, you come with me and HiLo. Well see if those Galrogs will listen to sense.”

Slash tells the other Brothers where to look and where to check back.

We say good-bye. We find the stairs to the nearest subtunnel and go down into lobbies full of shadow, where bodies lie waiting for the last train.

We race rats down the tunnel. They are meaner and fatter than ever, but our lights hold them back.

“Still got that wicked blade?” goes Slash.

“This baby?” HiLo swings his good arm, and a scalpel blade drops into his hand.

Slash's eyes frost over, and his mouth tightens.

“May need it,” he goes.

“Right, Brother.” HiLo makes the blade disappear.

I see that is how it has to be.

We pass a few more lobbies before going up and out. We've moved faster than we could have on ground; now we are close to the low end of Fun City.

“This way.” HiLo points past broken hives. I see codes scripted on the rubbled walls: Galrog signals?
“Wait,” goes Jade. “I'm starved.”

There is a liquor store a block away. We lift the door and twist it open, easy as breaking an arm. Nothing moves inside or on the street as our lights glide over rows of bottles. Broken glass snaps under our sneakers. The place smells drunk, and I'm getting that way from breathing. We find chips and candy bars that have survived under a counter, and we gulp them down in the doorway.

“So where's the Galrog hideaway?” goes Jade, finishing a Fifth Avenue bar.

Just then we feel that little deep tug. This one whispers death. A team is letting us know that it has us surrounded.

HiLo goes, “Duck back.”

“No,” goes Slash. “No more hiding.”

We go slow to the door and look through. Shadows peel from the walls and streak from alley mouths. We're sealed tight.

“Keep your blades back, Brothers.”

I never smashed with Galrogs; I see why Slash kept us away. They are tanked out with daystars, snappers, guns, and glory-stix. Even unarmed they would be fierce, with their fire-painted eyes, chopped topknots a dozen colors, and rainbow geometries tattooed across their faces. Most are dressed in black; all are on razor-toed roller skates.
Their feelings are masked from us behind a mesh of silent threats.

A low voice: “Come out if you plan to keep breathing.”

We move out, keeping together as the girls close tight. Jade raises his flashlight, but a Galrog with blue-triangled cheeks and purple-blond topknot kicks it from his hand. It goes spinning a crazy beam through his dark. There is not a scratch on Jade's fingers. I keep my own light low.

A big Galrog rolls up. She looks like a cognibot slung with battery packs, wires running up and down her arms and through her afro, where she's hung tin bells and shards of glass. She has a laser turret strapped to her head and a snapper in each hand.

She checks me and Jade over and out, then turns toward the slickers.

“Slicker HiLo and Slicker Slash,” she goes. “Cute match, but I thought Soooooots were hot for girlies.”

“Keep it short, Bala,” goes Slash. “The blocs are smashed.”

“So I see.” She smiles with black, acid-etched teeth. “Hevvies got stomped next door, and we got a new playground.”
“Have fun playing for a day or two,” goes HiLo. “The ones who squelched them are coming back for you.”

“Buildings squashed them. The end of the ramming world has been and gone. Where were you?”

“There's a new team playing in Fun City,” HiLo goes.

Bala's eyes turn to slits. “Ganging on us now, huh? That's a getoff.”

“The Four Hundred Boys,” goes Jade.

“Enough to keep you busy!” She laughs and skates a half-circle. “Maybe.”

“They're taking Fun City for their bloc—maybe all of it. They don't play fair. Those Boys never heard of clean fun.”

“Skud,” she goes, and shakes her hair so tin bells shiver. “You blew cirks, kids.”

Slash knows that she is listening. “We're calling all teams, Bala. We gotta save our skins now, and that means we need to find more hideaways, let more slickers know what's up. Are you in or out?”

HiLo goes, “They smashed the Soooooots in thirty seconds flat.”

A shock wave passes down the street like the tail end of a whiplash from center city. It catches us all by surprise and our guards go down; Galrogs, Brothers, Soooooot—we are all afraid of those wreckers. It unites us just like that.

When the shock passes we look at one another with wide eyes.

All the unspoken Galrog threats are gone. We have to hang together.

“Let's take these kids home,” goes Bala.

“Yeah, Mommy!”

With a whisper of skates, the Galrogs take off.

Our well-armed escort leads us through a maze of skate trails cleared in rubble.

“Boys, huh?” I hear Bala say to the other slickers. “We thought different.”

“What did you think?”

“Gods,” Bala goes.

“Gods!”

“God-things, mind-stuff. Old Mother looked into her mirror and saw a bonfire made out of cities. Remember before the blister tore? There were wars in the south, weirdbombs going off like firecrackers. Who knows what kind of stuff was cooking in all that blaze? “Old Mother said it was the end of the world, time for the ones outside to come through the cracks. They scooped all that energy and molded it into mass. Then they started scaring up storms, smashing. Where better to smash than Fun City?”

“End of the world?” goes HiLo. “Then why are we still here?”

Bala laughs. “You doob, how did you ever get to be a slicker? Nothing ever ends. Nothing.”

In ten minutes we come to a monstermart pyramid with its lower mirror windows put back together in jigsaw shards. Bala gives a short whistle, and double doors swing wide.

In we go.

The first thing I see are boxes of supplies heaped in the aisles, cookstoves burning, cots, and piles of blankets. I also spot a few people who can't be Galrogs—like babies and a few grownups.

“We've been taking in survivors,” goes Bala. “Old Mother said that we should.” She shrugs.

Old Mother is ancient, I have heard. She lived through the plagues and came out on the side of the teams. She must be upstairs, staring in her mirror, mumbling.

Slash and HiLo look at each other. I cannot tell what they are thinking. Slash turns to me and Jade.
“Okay, Brothers, we've got work to do. Stick around.”

“Got anywhere to sleep?” Jade goes. The sight of all those cots and blankets made both of us feel tired.
Bala points at a dead escalator. “Show them the way, Shell.”

The Galrog with a blond topknot that's streaked purple speeds down one aisle and leaps the first four steps of the escalator. She runs to the top without skipping a stroke and grins down from above.

“She's an angel,” goes Jade.

There are more Galrogs at the top. Some girls are snoring along the walls.

Shell cocks her hips and laughs. “Never seen Brothers in a monstermart before.”

“Aw, my ma used to shop here,” goes Jade. He checks her up and over.

“What'd she buy? Your daddy?”

Jade sticks his thumb through his fist and wiggles it with a big grin. The other girls laugh but not Shell. Her blue eyes darken and her cheeks redden under the blue triangles. I grab Jade's arm.

“Don't waste it,” goes another Galrog.

“I'll take the tip off for you,” goes Shell, and flashes a blade. “Nice and neat.”

I tug Jade's arm, and he drops it.

“Come on, grab blankets,” goes Shell. “You can bed over there.”

We take our blankets to a corner, wrap up, and fall asleep close together. I dream of smoke.

It is still dark when Slash wakes us.

“Come on, Brothers, lots of work to do.”

Things have taken off, we see. The Galrogs know the hideaways of more teams than we ever heard of, some from outside Fun City. Runners have been at it all night, and things are busy now.

From uptown and downtown in a wide circle around 400th, they have called all who can come.

The false night of smoke goes on and on, no telling how long. It is still dark when Fun City starts moving.

Over hive and under street, by sewer, strip, and alleyway, we close in tourniquet-tight on 400th, where Soooooots ran a clean-fun bloc. From 1st to 1000th, Bayview Street to Riverrun Boulevard, the rubble scatters and the subtunnels swarm as Fun City moves. Brothers and Galrogs are joined by Ratbeaters, Drummers, Myrmies, and Kingpins, from Piltdown, Renfrew, and the Upperhand Hills. The Diablos cruise down with Chogs and Cholos, Sledges and Trimtones, JipJaps and A-V-Marias. Tints, Chix, RockoBoys, Gerlz, Floods, Zips, and Zaps. More than I can remember.

It is a single team, the Fun City team, and all the names mean the same thing.

We Brothers walk shoulder to shoulder, with the last Soooooot among us.

Up the substairs we march to a blasted black surface. It looks like the end of the world, but we are still alive. 
I can hardly breathe for a minute, but I keep walking and let my anger boil.

Up ahead of us the Four Hundred Boys quiet down to a furnace roar.

By 395th we have scattered through cross streets into the Boys' bloc.
When we reach 398th fire flares from hives ahead. There is a sound like a skyscraper taking its first step. A scream echoes high between the towers and falls to the street.

At the next corner, I see an arm stretched out under rubble. Around the wrist the cuff is jagged black and red.

“Go to it,” goes HiLo.

We step onto 400th and stare forever. I'll never forget.

The streets we knew are gone. The concrete has been pulverized to gravel and dust, cracked up from underneath. Pyramid hives are baby volcano cones that hack smoke, ooze fire, and burn black scars in the broken earth. Towers hulk around the spitting volcanoes like buildings warming themselves under the blanked-out sky.

Were the Four Hundred Boys building a new city? If so, it would be much worse than death.

Past the fires we can see the rest of Fun City. We feel the team on all sides, a pulse of life connecting us, one breath.

HiLo has seen some of this before, but not all. He sheds no tears tonight.

He walks out ahead of us to stand black against the flames. He throws back his head and screams: “Heeeeeey!”

A cone erupts between the monster buildings. It drowns him out; so he shouts even louder.

“Hey, you Four Hundred Boys!”

Shattered streetlights pop half to life. Over my head one explodes with a flash.

“This is our bloc, Four Hundred Boys!”

Galrogs and Trimtones beat on overturned cars. It gets my blood going.

“So you knocked in our hives, you Boys. So you raped our city.”

Our world. I think of the moon, and my eyes sting.

“So what?”

The streetlights black out. The earth shudders. The cones roar and vomit hot blood all over those buildings; I hear it sizzle as it drips.

Thunder talks among the towers.

“I bet you will never grow UP!”

Here they come.

All at once there are more buildings in the street. I had thought they were new buildings, but they are big Boys. Four hundred at least.

“Stay cool,” goes Slash.

The Four Hundred Boys thunder into our streets.

We move back through shadows into hiding places only we can reach.

The first Boys swing chains with links the size of skating rinks. Off come the tops of some nearby hives. The Boys cannot quite get at us from up there, but they can cover us with rubble.

They look seven or eight years old for all their size, and there is still baby pudge on their long, sweaty faces. Their eyes have a vicious shine like boys that age get when they are pulling the legs off a bug—laughing wild but freaked and frightened by what they see their own hands doing. They look double deadly because of that. They are on fire under their skin, fever yellow.

They look more frightened than us. Fear is gone from the one team. We reach out at them as they charge, sending our power from all sides. We chant, but I do not know if there are any words; it is a cry. It might mean, “Take us if you can, Boys; take us at our size.”

I feel as if I have touched a cold, yellow blaze of fever; it sickens me, but the pain lets me know how real it is. I find strength in that; we all do. We hold onto the fire, sucking it away, sending it down through our feet into the earth.

The Boys start grinning and squinting. They seem to be squeezing inside out. The closest ones start shrinking, dropping down to size with every step.

We keep on sucking and spitting the fever. The fire passes through us. Our howling synchronizes.

The Boys keep getting smaller all the time, smaller and dimmer. Little kids never know when to stop. Even when they are burned out, they keep going.

As we fall back the first Boy comes down to size. One minute he is taller than the hives; then he hardly fills the street. A dozen of his shrinking pals fill in on either side. They whip their chains and shriek at the sky like screaming cutouts against the downtown fires.

They break past HiLo in the middle of the street and head for us. Now they are twice our size … now just right.

This I can handle.

“Smash!” yells Slash.

One Boy charges me with a wicked black curve I can't see till it's whispering in my ear. I duck fast and come up faster where he doesn't expect me.

He goes down soft and heavy, dead. The sick, yellow light throbs out with his blood, fades on the street.

I spin to see Jade knocked down by a Boy with an ax. There is nothing I can do but stare as the black blade swings high.

Shrill whistle. Wheels whirring.

A body sails into the Boy and flattens him out with a footful of razors and ballbearings. Purple-blond topknot and a big grin. The Galrog skips high and stomps his hatchet hand into cement, leaving stiff fingers curling around mashed greenish blood and bones.

Shell laughs at Jade and takes off.

I run over and yank him to his feet. Two Boys back away into a dark alley that lights up as they go in. We start after, but they have already been fixed by Quazis and Drummers lying in wait.

Jade and I turn away.

HiLo still stares down the street. One Boy has stood tall, stronger than the rest and more resistant to our power. He raps a massive club in his hand.

“Come on, slicker” HiLo calls. “You remember me, don't you?"

The biggest of the Boys comes down, eating up the streets. We concentrate on draining him, but he shrinks more slowly than the others.

His club slams the ground. Boom! Me and some Galrogs land on our asses. The club creases a hive, and cement sprays over us, glass sings through the air.

HiLo does not move. He waits with red-and-black lightning bolts serene, both hands empty.

The big slicker swings again, but now his head only reaches to the fifth floor of an Rx. HiLo ducks as the club streaks over and turns a storefront window into dust.

The Soooooot's scalpel glints into his hand. He throws himself at the Boy's ankle and grabs on tight.

He slashes twice. The Boy screams like a cat. Neatest hamstringing you ever saw.

The screaming Boy staggers and kicks out hard enough to flip HiLo across the street into the metal cage of a shop window. HiLo lands in a heap of impossible angles and does not move again. Slash cries out. His gun shouts louder. One blood-silver shot. It leaves a shining line in the smoky air.

The Boy falls over and scratches the cement till his huge fingertips bleed. His mouth gapes wide as a manhole, his eyes stare like the broken windows all around. His pupils are slit like a poison snake's, his face long and dark, hook-nosed.

God or boy, he is dead. Like some of us.

Five Drummers climb over the corpse for the next round, but with their slickie dead the Boys are not up to it. The volcanoes belch as though they too are giving up.

The survivors stand glowing in the middle of their bloc. A few start crying, and that is a sound I cannot spell. It makes Crybaby start up. He sits down in cement, sobbing through his fingers. His tears are the color of an oil rainbow on wet asphalt.

We keep on sucking up the fever glow, grounding it all in the earth.

The Boys cry louder, out of pain. They start tearing at each other, running in spirals, and a few leap into the lava that streams from the pyramids.

The glow shrieks out of control, out of our hands, gathering between the Boys with its last strength—ready to pounce.

It leaps upward, a hot snake screaming into the clouds.

Then the Boys drop dead and never move again.

A hole in the ceiling of smoke. The dark-blue sky peeks through, turning pale as the smoke thins. The Boys' last scream dies out in the dawn.

The sun looks bruised, but there it is. Hiya up there!

“Let's get to it,” goes Slash. “Lots of cleanup ahead.” He has been crying. I guess he loved HiLo like a Brother. I wish I could say something.

We help one another up. Slap shoulders and watch the sun come out gold and orange and blazing white. I don't have to tell you it looks good, teams.