\chapter{Acknowledgements}

Mirrorshades anthology copyright © 1986 by Bruce Sterling. \\
“The Gernsback Continuum” by William Gibson. Copyright © 1981 by Terry Carr. First published in Universe 11. \\
“Snake-Eyes” by Tom Maddox. Copyright © 1986 by Omni Publications International Ltd. First published in Omni April 1986. \\
“Rock On” by Pat Cadigan. Copyright © 1984 by Pat Cadigan. First published in Light Years and Dark (Berkley). \\
“Tales of Houdini” by Rudy Rucker. Copyright © 1983 by Rudy Rucker. First published in Elsewhere (Ace). \\
“400 Boys” by Marc Laidlaw. Copyright © 1983 by Omni Publications International Ltd. First published in Omni, November 1983. \\
“Solstice” by James Patrick Kelly. Copyright © 1985 by Davis Publications, Inc. First published in Isaac Asimov's Science Fiction Magazine, June 1985. \\
“Petra” by Greg Bear. Copyright © 1982 by Greg Bear. First published in Omni, February 1982. \\
‘Till Human Voices Wake Us” by Lewis Shiner. Copyright © 1984 by Mercury Press, Inc. First published in The Magazine of Fantasy and Science Fiction, May 1984. \\
“Freezone” by John Shirley. Copyright © 1985 by John Shirley. First published in Eclipse (Bluejay). \\
“Stone Lives” by Paul Di Filippo. Copyright © 1985 by Mercury Press, Inc. First published in The Magazine of Fantasy and Science Fiction, August 1985. \\
“Red Star, Winter Orbit” by Bruce Sterling and William Gibson. Copyright © 1983 by Omni Publications International Ltd. First published in Omni, July 1983. Reprinted by permission of the authors. \\
“Mozart in Mirrorshades” by Bruce Sterling and Lewis Shiner. Copyright © 1985 by Omni Publications International Ltd. First published in Omni, September 1985. Reprinted by permission of the authors. \\
“Freezone”* extracted from Eclipse, Copyright © 2012 by John Shirley. "Freezone (Original Version)" Copyright © John Shirley 1986, John Shirley and Paula Guran. \\
“Snake Eyes” by Tom Maddox is released under a Creative Commons License: http://creativecommons.org/licenses/by-nd-nc/1.0/ \\
“Rock On,” by Pat Cadigan. Copyright © 1984 by Pat Cadigan. First published in Light Years And Dark (Berkley). \\
“Tales of Houdini” appears in Complete Stories Copyright © 2016 Rudy Rucker “400 Boys” copyright 1983 by Marc Laidlaw. First appeared in Omni Magazine, November 1983. \\
“Solstice,” by James Patrick Kelly. Copyright © 1985 by Davis Publications, Inc. First published in Isaac Asimov’s Science Fiction Magazine, June 1985. \\
“Petra” Copyright © 2004 by Greg Bear, “Petra” copyright © 1981 by Omni Publications International, Ltd. for Omni. \\
“Till Human Voices Wake Us” © 1984 by Mercury Press, Inc. First published in The Magazine of Fantasy and Science Fiction, May 1984. Some rights reserved. \\
“Stone Lives” first appeared in The Magazine of Fantasy and Science Fiction in 1985. \\
‘Red Star, Winter Orbit’; © by Omni Publications International Ltd, 1983. Appears in Burning Chrome, Copyright © William Gibson 1986. \\
“Mozart in Mirrorshades” is © 1985 by Omni Publications International Ltd. First published in Omni, September, 1985.