\chapter{Rock On}
\chapterauthor{Pat Cadigan}

Pat Cadigan's career began with the decade. Her work hasshown wide variety, ranging through dark fantasy and horror toquirky and original science fiction.

Cadigan's style is often marked by a tough-minded vigor and icy undercurrents of black humor—an Eighties sensibility that can only be called punk. Her ``Pathosfinder series'' (including such stories as ``Nearly Departed'') was remarkable for its eerily visionary air.

Cadigan's multifaceted talent includes a strong gift for definitive hard-core cyberpunk. This story; which appeared in 1985, is an outright collision of high tech and the rock under ground.

Her first novel is \textit{The Pathosfinder}. She lives in Kansas.

\hrulefill

\firstletter{R}ain woke me. I thought, shit, here I am, Lady Rain-in-the-Face, because that's where it was hitting, right in the old face. Sat up and saw I was still on Newbury Street. See beautiful downtown Boston. Was Newbury Street downtown? In the middle of the night, did it matter? No, it did not. And not a soul in sight. Like everybody said, let's get Gina drunk and while she's passed out, we'll all move to Vermont. Do I love New England? A great place to live, but you wouldn't want to visit here.

I smeared my hair out of my eyes and wondered if anyone was looking for me now. Hey, anybody shy a forty-year-old rock `n' roll sinner?

I scuttled into the doorway of one of those quaint old buildings where there was a shop with the entrance below ground level. A little awning kept the rain off but pissed water down in a maddening beat. Wrung the water out of my wrap-pants and my hair and just sat being damp. Cold, too, I guess, but didn't feel that so much.

Sat a long time with my chin on my knees: you know, it made me feel like a kid again. When I started nodding my head, I began to pick up on something. Just primal but I tap into that amazing well. Man-O-War, if you could see me now. By the time the blueboys found me, I was rocking pretty good.

And that was the punchline. I'd never tried to get up and leave, but if I had, I'd have found I was locked into place in a sticky field. Made to catch the b\&e kids in the act until the blueboys could get around to coming out and getting them. I'd been sitting in a trap and digging it. The story of my life.

\fancybreak{* * *}

They were nice to me. Led me, read me, dried me out. Fined me a hundred, sent me on my way in time for breakfast.

Awful time to see and be seen, righteous awful. For the first three hours after you get up, people can tell whether you've got a broken heart or not. The solution is, either you get up \textit{real} early so your camouflage is in place by the time everybody else is out, or don't go to bed. Don't go to bed ought to work all the time, but it doesn't. Sometimes when you don't go to bed, people can see whether you've got a broken heart all day long. I schlepped it, searching for an uncrowded breakfast bar and not looking at anyone who was looking at me. But I had this urge to stop random pedestrians and say, Yeah, yeah, it's true, but it was rock `n' roll broke my poor old heart, not a person, don't cry for me or I'll pop your chocks.

I went around and up and down and all over until I found Tremont Street. It had been the pounder with that group from the Detroit Crater—the name was gone but the malady lingered on—anyway, him, he'd been the one told me Tremont had the best breakfast bars in the world, especially when you were coming off a bottle-drunk you couldn't remember.

When the c'muters cleared out some, I found a space at a Greek hole-in-the-wall. We shut down 10:30 A.M. sharp, get the hell out when you're done, counter service only, take it or shake it. I like a place with Attitude. I folded a seat down and asked for coffee and a feta cheese omelette. Came with home fries from the home fries mountain in corner of the grill (no microwave \textit{gar-bazhe}, hoo-ray). They shot my retinas before they even brought my coffee, and while I was pouring the cream, they checked my credit. Was that badass? It was badass. Did I care? I did not. No waste, no machines when a human could do it, and real food, none of this edible polyester that slips clear through you so you can stay looking like a famine victim, my deah.

They came in when I was half-finished with the omelette. Went all night by the look and sound of them, but I didn't check their faces for broken hearts. Made me nervous but I thought, well, they're tired; who's going to notice this old lady? Nobody.

Wrong again. I became visible to them right after they got their retinas shot. Seventeen-year-old boy with tattooed cheeks and a forked tongue leaned forward and hissed like a snake.

``Sssssssinner.''

The other four with him perked right up. ``Where?'' ``Whose?'' ``In here?''

``Rock `n' roll ssssssinner.''

The lady identified me. She bore much resemblance to nobody at all, and if she had a heart it wasn't even sprained a little. With a sinner, she was probably Madame Magnifica. ``Gina,'' she said, with all confidence.

My left eye tic'd. Oh, please. Feta cheese on my knees. What the hell, I thought, I'll nod, they'll nod, I'll eat, I'll go. And then somebody whispered the word, \textit{reward}.

I dropped my fork and ran.

Safe enough, I figured. Were they all going to chase me before they got their Greek breakfasts? No, they were not. They sent the lady after me.

She was much the younger, and she tackled me in the middle of a crosswalk when the light changed. A car hopped over us, its undercarriage just ruffling the top of her hard copper hair.

``Just come back and finish your omelette. Or we'll buy you another.''

``No.''

She yanked me up and pulled me out of the street. ``Come on.'' People were staring but Tremont's full of theatres. You see that here, live theatre, you can still get it. She put a bring-along on my wrist and brought me along, back to the breakfast bar, where they'd sold the rest of my omelette at a discount to a bum. The lady and her group made room for me among themselves and bought me another cup of coffee.

``How can you eat and drink with a forked tongue?'' I asked Tattooed Cheeks. He showed me. A little appliance underneath, like a \textit{zipper}. The Featherweight to the left of the big boy on the lady's other side leaned over and frowned at me.

``Give us one good reason why we shouldn't turn you in for Man-O-War's reward.''

I shook my head. ``I'm through. This sinner's been absolved.''

``You're legally bound by contract,'' said the lady. ``But we could c'noodle something. Buy Man-O-War out, sue on your behalf for nonfulfillment. We're Misbegotten. Oley.'' She pointed at herself. ``Pidge.'' That was the silent type next to her. ``Percy.'' The big boy. ``Krait.'' Mr. Tongue. ``Gus.'' Featherweight. ``We'll take care of you.''

I shook my head again. ``If you're going to turn me in, turn me in and collect. The credit ought to buy you the best sinner ever there was.''

``We can be good to you.''

``I don't have it any more. It's gone. All my rock `n' roll sins have been forgiven.''

``Untrue,'' said the big boy. Automatically, I started to picture on him and shut it down hard. ``Man-O-War would have thrown you out if it were gone. You wouldn't have run.''

``I didn't want to tell him. Leave me alone. I just want to go and sin no more, see? Play with yourselves, I'm not helping.'' I grabbed the counter with both hands and held on. So what were they going to do, pop me one and carry me off?

As a matter of fact, they did.

In the beginning, I thought, and the echo effect was stupendous. \textit{In the beginning ... the beginning ... the beginning ...}

In the beginning, the sinner was not human. I know because I'm old enough to remember.

They were all there, little more than phantoms. Misbegotten. Where do they get those names? I'm old enough to remember. Oingo-Boingo and Bow-Wow-Wow. Forty, did I say? Oooh, just a little past, a little close to a lot. Old rockers never die, they just keep rocking on. I never saw The Who, Moon was dead before I was born. But I remember, barely old enough to stand, rocking in my mother's arms while thousands screamed and clapped and danced in their seats. \textit{Start me up ... if you start me up, I'll never stop ...} 763 Strings did a rendition for elevator and dentist's office, I remember that, too. And that wasn't the worst of it.

They hung on the memories, pulling more from me, turning me inside out. Are you experienced? Only a record of my father's because he'd died, too, before my parents even met and nobody else ever dared ask that question. \textit{Are you experienced? ... Well, I am.}

(Well, \textit{I} am.)

Five against one and I couldn't push them away. Only, can you call it rape when you know you're going to like it? Well, if I couldn't get away, then I'd give them the ride of their lives. \textit{Jerkin' Crocus didn't kill me but she sure came near ...} .

The big boy faded in first, big and wild and too much badass to him. I reached out, held him tight, showing him. The beat from the night in the rain, I gave it to him, fed it to his heart and made him live it. Then came the lady, putting down the bass theme. She jittered, but mostly in the right places.

Now the Krait, and he was, slithering around the sound, in and out. Never mind the tattooed cheeks, he wasn't just flash for the fools. He knew; you wouldn't have thought it, but he knew.

Featherweight and the silent type, melody and first harmony. Bad. Featherweight was a disaster, didn't know where to go or what to do when he got there, but he was pitching ahead like the \textit{S.\ S.\ Suicide}.

Christ. If they had to rape me, couldn't they have provided someone upright? The other four kept on, refusing to lose it, and I would have to make the best of it for all of us. Derivative, unoriginal—Featherweight did not rock. It was a crime, but all I could do was take them and shake them. Rock gods in the hands of an angry sinner.

They were never better. Small change getting a glimpse of what it was like to be big bucks. Hadn't been for Featherweight, they might have gotten all the way there. More groups now than ever there was, all of them sure that if they just got the right sinner with them, they'd rock the moon down out of the sky.
We maybe vibrated it a little before we were done. Poor old Featherweight.

I gave them better than they deserved, and they knew that, too. So when I begged out, they showed me respect at last and went. Their techies were gentle with me, taking the plugs from my head, my poor old throbbing abused broken-hearted sinning head, and covered up the sockets. I had to sleep and they let me. I hear the man say, ``That's a take, righteously. We'll rush it into distribution. Where in \textit{hell} did you find that sinner?''
``Synthesizer,'' I muttered, already asleep. ``The actual word, my boy, is synthesizer.''

\fancybreak{* * *}

Crazy old dreams. I was back with Man-O-War in the big CA, leaving him again, and it was mostly as it happened, but you know dreams. His living room was half outdoors, half indoors, the walls all busted out. You know dreams; I didn't think it was strange.

Man-O-War was mostly undressed, like he'd forgotten to finish. Oh, that never happened. Man-O-War forget a sequin or a bead? He loved to act it out, just like the Krait.

``No more,'' I was saying, and he was saying, ``But you don't know anything else, you shitting?'' Nobody in the big CA kids, they all shit; loose juice.

``Your contract goes another two and I get the option, I always get the option. And you love it, Gina, you know that, you're no good without it.''

And then it was flashback time and I was in the pod with all my sockets plugged, rocking Man-O-War through the wires, giving him the meat and bone that made him Man-O-War and the machines picking it up, sound and vision so all the tube-babies all around the world could play it on their screens whenever they wanted. Forget the road, forget the shows, too much trouble, and it wasn't like the tapes, not as exciting, even with the biggest FX, lasers, spaceships, explosions, no good. And the tapes weren't as good as the stuff in the head, rock `n' roll visions straight from the brain. No hours of set-up and hours more doctoring in the lab. But you had to get everyone in the group dreaming the same way. You needed a synthesis, and for that you got a synthesizer, not the old kind, the musical instrument, but something—somebody—to channel your group through, to bump up their music and their tube-fed little souls, to rock them and roll them the way they couldn't do themselves. And anyone could be a rock `n' roll hero then. Anyone!

In the end, they didn't have to play instruments unless they really wanted to, and why bother? Let the synthesizer take their imaginings and boost them up to Mount Olympus.

Synthesizer. Synner. Sinner.

Not just anyone can do that, sin for rock `n' roll. I can.

But it's not the same as jumping all night to some bar band nobody knows yet ... Man-O-War and his blown-out living room came back, and he said, ``You rocked the walls right out of my house. I'll never let you go.''
And I said, ``I'm gone.''

Then I was out, going fast at first because I thought he'd be hot behind me. But I must have lost him and then somebody grabbed my ankle.

\fancybreak{* * *}

Featherweight had a tray, like he was Mr. Nursie-Angel-of-Mercy. Nudged the foot of the bed with his knee, and it sat me up slow. She rises from the grave, you can't keep a good sinner down.

``Here.'' He set the tray over my lap, pulled up a chair. Some kind of thick soup in a bowl he'd given me, with veg wafers to break up and put in. ``Thought you'd want something soft and easy.'' He put his left foot up on his right leg and had a good look at it. ``I \textit{never} been rocked like that before.''

``You don't have it, no matter who rocks you ever in this world. Cut and run, go into management. The \textit{big} Big Money's in management.''

He snacked on his thumbnail. ``Can you always tell?''

``If the Stones came back tomorrow, you couldn't even tap your toes.''

``What if you took my place?''

``I'm a sinner, not a clown. You can't sin and do the dance. It's been tried.''

``\textit{You} could do it. If anyone could.''

``No.''

His stringy cornsilk fell over his face and he tossed it back. ``Eat your soup. They want to go again shortly.''
``No.'' I touched my lower lip, thickened to sausage size. ``I won't sin for Man-O-War and I won't sin for you. You want to pop me one again, go to. Shake a socket loose, give me aphasia.''

So he left and came back with a whole bunch of them, techies and do-kids, and they poured the soup down my throat and gave me a poke and carried me out to the pod so I could make Misbegotten this year's firestorm.

I knew as soon as the first tape got out, Man-O-War would pick up the scent. They were already starting the machine to get me away from him. And they kept me good in the room—where their old sinner had done penance, the lady told me. Their old sinner came to see me, too. I thought, poison dripping from his fangs, death threats. But he was just a guy about my age with a lot of hair to hide his sockets (I never bothered, didn't care if they showed). Just came to pay his respects, how'd I ever learn to rock the way I did?

Fool.

They kept me good in the room. Drunks when I wanted them and a poke to get sober again, a poke for vitamins, a poke to lose the bad dreams. Poke, poke, pig in a poke. I had tracks like the old B\&O, and they didn't even know what I meant by that. They lost Featherweight, got themselves someone a little more righteous, someone who could go with it and work out, sixteen-year-old snip girl with a face like a praying mantis. But she rocked and they rocked and we all rocked until Man-O-War came to take me home.

Strutted into my room in full plumage with his hair all fanned out (hiding the sockets) and said, ``Did you want to press charges, Gina darling?''

Well, they fought it out over my bed. When Misbegotten said I was theirs now, Man-O-War smiled and said, ``Yeah, and I bought \textit{you}. You're \textit{all} mine now, you and your sinner. My sinner.'' That was truth. Man-O-War had his conglomerate start to buy Misbegotten right after the first tape came out. Deal all done by the time we'd finished the third one and they never knew. Conglomerates buy and sell all the time. Everybody was in trouble but Man-O-War. And me, he said. He made them all leave and sat down on my bed to re-lay claim to me.

``Gina.'' Ever see honey poured over the edge of a saw-tooth blade? Ever hear it? He couldn't sing without hurting someone bad and he couldn't dance, but inside, he rocked. If I rocked him.

``I don't want to be a sinner, not for you or anyone.''

``It'll all look different when I get you back to Cee-Ay.''

``I want to go to a cheesy bar and boogie my brains till they leak out the sockets.''

``No more, darling. That was why you came here, wasn't it? But all the bars are gone and all the bands. Last call was years ago, it's all up here now. All up here.'' He tapped his temple. ``You're an old lady, no matter how much I spend keeping your bod young. And don't I give you everything? And didn't you say I had it?''

``It's not the same. It wasn't meant to be put on a tube for people to \textit{watch}.''

``But it's not as though rock `n' roll is dead, lover.''

``You're killing it.''

``Not me. You're trying to bury it alive. But I'll keep you going for a long, long time.''

``I'll get away again. You'll either rock 'n' roll on your own or give it up, but you won't be taking it out of me any more. This ain't my way, it ain't my time. Like the man said, `I don't live today.'''

Man-O-War grinned. ``And like the other man said, `Rock `n' roll never forgets.'''

He called in his do-kids and took me home.
