\chapter{Stone Lives}
\chapterauthor{Paul di Filippo}

Paul Di Filippo is a newly published writer whose body of work is still small. Yet his work is already attracting attention for its ambitious scope and weirdly visionary imagery.

The following piece, which appeared in 1985, was his third published story. With its theme of transformation, radical social change, and the impact of new technologies, it demonstrates Di Filippo's firm grasp of the cyberpunk dynamic. He lives in Providence, Rhode Island.

\hrulefill

\firstletter{O}dors boil around the Immigration Offices, a stenchy soup. The sweat of desperate men and women, ripe garbage strewn in the packed street, the spicy scent worn by one of the guards at the outer door. The mix is heady, almost overpowering to anyone born outside the Bungle, but Stone is used to it. The constant smells constitute the only atmosphere he has ever known, his native element, too familiar to be despised.

Noise swells to rival the stench. Harsh voices raised in dispute, whining voices lowered to entreat. ``Don't sluff me, you rotty bastard!'' ``l'd treat you real nice, honey, for a share of that.'' From the vicinity of the door into Immigration, an artificial voice is reciting the day's job offerings, cycling tirelessly through the rotty choices.

``---to test new aerosol antipersonnel toxins. 4M will contract to provide survivors with a full Citrine rejuve. High-orbit vakheads needed by McDonnell Douglas. Must be willing to be imprinted---''

No one seems eager to rush forward and claim these jobs. No voices beg the guards for entrance. Only those who have incurred impossible debts or enmity inside the Bungle ever take a chance on the Rating-10 assignments, which are Immigation's disdainful handouts. Stone knows for sure that he wants no part of these rigged propositions. Like all the rest, he is here at Immigration simply because it provides a focal point, a gathering place as vital as a Serengeti water hole, where the sneaky sluffs and raw deals that pass for business in the South Bronx FEZ---a.k.a. the Bronx Jungle, a.k.a. the Bungle---can he transacted.

Heat smites the noisy crowd, making them more irritable than usual---a dangerous situation. Hyperalertness parches Stone's throat. He reaches for the scratched-to-his-touch plastic flask at his hip and swigs some stale water. Stale but safe, he thinks, relishing his secret knowledge. It was pure luck that he ever stumbled upon the slow leak in the inter-FEZ pipe down by the river fence that encircles the Bungle. He smelled the clean water like a dog from a distance, and by running his hands along several meters of chilly pipe, he found the drip. Now he has all the manifold cues to its exact location deeply memorized.

Shuffling through the crowd on bare calloused feet (amazing what information can he picked up through the soles to keep body and soul intact!), Stone quests for scraps of information that will help him survive another day in the Bungle. Survival is his main---his only---concern. If Stone has any pride left, after enduring what he has endured, it is pride in surviving.

A brassy voice claims, ``I booted some tempo, man, and that was the end of that fight. Thirty seconds later, all three're dead.'' A listener whistles admiringly. Stone imagines he latches on somehow to a boot of tempo and sells it for an enormous profit, which he them spends on a dry, safe place to sleep and enough to fill his ever-empty gut. Not damn likely, but a nice dream nonetheless.

Thought of food causes his stomach to churn. Across the rough, encrusted cloth covering his midriff, he rests his right hand with its sharp lance of pain that marks the infected cut. Stone assumes the infection. He has no way of telling for sure until it begins to stink.

Stone's progress through the babble of voices and crush of flesh has brought him fairly close to the entrance to Immigration. He feels a volume of empty air between the crowds and the guards, a quartersphere of respect and fear, its vertical face the wall of the building. The respect is generated by the employed status of the guards; the fear by their weapons.

Someone---a transported felon with a little education---once described the guns to Stone. Long, bulky tubes with a bulge halfway along their length where the wiggler magnets are. Plastic stocks and grips. They emit charged beams of energetic electrons at relativistic speeds. If the scythe of the beam touches you, the kinetic energy imparted blows you apart like a squashed sausage. If the particle beam chances to miss, the accompanying cone of gamma rays produces radiation sickness that is fatal within hours.

Of the explanation---which Stone remembers verbatim---he understands only the description of a horrible death. It is enough.

Stone pauses a moment. A familiar voice---that of Mary, the rat-seller---is speaking conspiratorially of the next shipment of charity clothes. Stone deduces her position as being on the very inner edge of the crowd. She lowers her voice. Stone can't make out her words, which are worth hearing. He edges forward, leery though he is of being trapped inside the clot of people--- A dead silence. No one is speaking or moving. Stone senses displaced air puff from between the guards: someone occupies the door.

``You.'' A refined woman's voice. ``Young man with no shoes, in the---'' Her voice hesitates for the adjective hiding beneath the grime. ``---red jumpsuit. Come here, please. I want to talk to you.''

Stone doesn't know if it is he (red?), until he feels the pressure of all eyes upon him. At once he pivots, swerves, fakes---but it is too late. Dozens of eager claws grab him. He wrenches. Moldy fabric splits, but the hands refasten on his skin. He bites, kicks, pummels. No use. During the struggle he makes no sound. Finally he is dragged forward, still fighting, past that invisible line that marks another world as surely as does the unbreachable fence between the Bungle and the other twenty-two FEZ.

Cinnamon scent envelops him, a guard holds something cold and metallic to the back of his neck. All the cells in his skull seem to flare at once, then darkness comes.

\fancybreak{* * *}

Three people betray their forms and locations to the awakened Stone by the air they displace, their scents, their voices---and by a fourth, subtle component he has always labeled sense-of-life.

Behind him: a bulky man who breathes awkwardly, no doubt because of Stone's ripe odor. This has to be a guard. To his left: a smaller person---the woman?---smelling like flowers. (Once Stone smelled a flower.) Before him, deskbound: a seated man.

Stone feels no aftereffects from the device used on him---unless the total disorientation that has overtaken him is it. He has no idea why he has been shanghaied, and wishes only to return to the known dangers of the Bungle.

But he knows they are not about to let him.

The woman speaks, her voice the sweetest Stone has ever heard.

``This man will ask you some questions. Once you answer them, I'11 have one for you. Is that all right?''

Stone nods, his only choice as he sees it.

``Name?'' says the Immigration official.

``Stone. ``

``That's all?''

``That's all anyone calls me.'' (Unbearable white-hot pain when they dug out the eyes of the little urchin they caught watching them carve up the corpse. But he never cried, oh, no; and so: Stone.) ``Place of birth?''

``This shitheap, right here. Where else?''

``Parents?''

``What're they?''

``Age?''

A shrug.

``That can be fixed later with a cellscan. I suppose we have enough to issue your card. Hold still now.''

Stone feels multiple pencils of warmth scroll over his face; seconds later, a chuntering sound from the desk.

``This is your proof of citizenship and access to the system. Don't lose it.''

Stone extends a hand in the direction of the voice, receives a plastic rectangle. He goes to shove it into a pocket, finds them both ripped away in the scuffle, and continues to hold the plastic awkwardly, as if it is a brick of gold about to be snatched away.

``Now my question.'' The woman's voice is like a distant memory Stone has of love. ``Do you want a job?''

Stone's trip wire has been brushed. A job they can't even announce in public? It must so fracking bad that it's off the common corporate scale.

``No thanks, miz. My life ain't much, but it's all I got.'' He turns to leave.

``Although I can't give you details until you accept, we'll register a contract right now that stipulates it's a Rating-1 job.''

Stone stops dead. It has to be a sick joke. But what if it's true?

``A contract?''

``Officer,'' the woman commands.

A key is tapped, and the desk recites a contract. To Stone's untutored ears, it sounds straightforward and without traps. A Rating-1 job for an unspecified period, either party able to terminate the contract, job description to be appended later.

Stone hesitates only seconds. Memories of all the frightful nights and painful days in the Bungle swarm in his head, along with the hot central pleasure of having survived. Irrationally, he feels a moment's regret at leaving behind the secret city spring he so cleverly found. But it passes.

``I guess you need this to O.K. it,'' Stone says, offering up his newly won card.

``I guess we do,'' the woman says with a laugh.

\fancybreak{* * *}

The quiet, sealed car moves through busy streets. Despite the lack of outside noise, the chauffeur's comments on the traffic and their frequent halts are enough to convey a sense of the bustling city around them.

``Where are we now?'' Stone asks for the tenth time. Besides wanting the information, he loves to hear this woman speak. Her voice, he thinks---its's like a spring rain when you're safe inside.

``Madison-Park FEZ, traveling crosstown.''

Stone nods appreciatively. She may as well have said, ``In orbit, blasting for the moon,'' for all the fuzzy mental image he gets.

Before they would let Stone leave, Immigration did several things to him. Shaved all his body hair off; deloused him; made him shower for ten minutes with a mildly abrasive soap; disinfected him; ran several instant tests; pumped six shots into him; and issued him underwear, clean coveralls, and shoes (shoes!) The alien smell of himself only makes the woman's perfume more at tractive. In the close confines of the backseat, Stone swims in it. Finally he can contain himself no longer.

``Uh, that perfume---what kind is it?''

``Lily of the valley.''

The mellifluous phrase makes Stone feel as if he is in another, kinder century. He swears he will always remember it. And he will.

``Hey!'' Consternation. ``I don't even know your name.''

``June. June Tannhauser.''

June. Stone. June and Stone and lilies of the valley. June in June with Stone in the valley with the lilies. It's like a song that won't cease in his head.

``Where are we going?'' he asks over the silent song in his head.

``To a doctor,'' says June.

``I thought that was all taken care of.''

``This man's a specialist. An eyespecialist.''

This is the final jolt, atop so many, knocking even the happy song out of Stone's head. He sits tense for the rest of the ride, unthinking.

\fancybreak{* * *}

``This is a lifesized model of what we're going to implant in you,'' the doctor says, putting a cool ball in Stone's hand.

Stone squeezes it in disbelief

``The heart of this eye system is CCD's---charge-coupled devices. Every bit of light---each photon---that hits them triggers one or more electrons. These electrons are collected as a continuous signal, which is fed through an interpreter chip to your optic nerves. The result: perfect sight.''

Stone grips the model so hard his palm bruises.

``Cosmetically, they're a bit shocking. In a young man like yourself, I'd recommend organic implants. However, I have orders from the person footing the bill that these are what you get. And of course, there are several advantages to them.''

When Stone does not ask what they are, the doctor continues anyway.

``By thinking mnemonic keywords that the chip is programmed for, you can perform several functions.

``One: You can store digitalized copies of a particular sight in the chip's RAM, for later display. When you reinvoke it with the keyword, it will seem as if you are seeing the sight again directly, no matter what you are actually looking at. Resumption of realtime vision is another keyword.

``Two: By stepping down the ratio of photons to electrons, you can do such things as stare directly at the sun or at a welder's flame without damage.

``Three: By upping the ratio, you can achieve a fair degree of normal sight in conditions such as a starry, moonless night.

``Four: For enhancement purposes, you can generate false-color images. Black becomes white to your brain, the old rose-colored glasses, whatever.

``And I think that about covers it.''

``What's the time frame on this, Doctor?'' June asks.

The doctor assumes an academic tone, obviously eager to show professional acumen. ``A day for the actual operation, two days, accelerated recovery, a week of training and further healing---say, two weeks, max.''

‘Very good,'' June says.

Stone feels her rise from the couch beside him, but remains seated.

``Stone,'' she says, a hand on his shoulder, ``time to go.''

But Stone can't get up, because the tears won't stop.

\fancybreak{* * *}

The steel and glass canyons of New York---that proud and flourishing union of Free Enterprise Zones---are a dozen shades of cool blue, stretching away to the north. The streets that run with geometric precision like distant rivers on the canyon floors are an arterial red. To the west and east, snatches of the Hudson River and the East River are visible as lime-green flows. Central Park is a wall of sunflower-yellow halfway up the island. To the northeast of the park, the Bungle is a black wasteland.

Stone savors the view. Vision of any kind, even the foggiest blurs, was an unthinkable treasure only days ago. And what he has actually been gifted with---this marvelous ability to turn the everyday world into a jeweled wonderland---is almost too much to believe. Momentarily sated, Stone wills his gaze back to normal. The city instantly reverts to its traditional color of steel-gray, sky-blue, tree-green. The view is still magnificent.

Stone stands at a bank of windows on the 150th floor of the Citrine Tower, in the Wall Street FEZ. For the past two weeks, this has been his home, from which he has not stirred. His only visitors have been a nurse, a cybertherapist, and June. The isolation and relative lack of human contact do not bother him. After the Bungle, such quiet is bliss. And then, of course, he has been enmeshed in the sensuous web of sight.

The first thing he saw upon waking after the operation set the glorious tone of his visual explorations. The smiling face of a woman hovered above him. Her skin was a pcllucid olive, her eyes a radiant brown, her hair a raven cascade framing her face.

``How are you feeling?'' June asked.

``Good,'' Stone said. Then he uttered a phrase he never had a use for before. ``Thank you.''

June waved a slim hand negligently. ``Don't thank me. I didn't pay for it.''

And that was when Stone learned that June was not his employer, that she worked for someone else. And although she wouldn't tell him then to whom he was indebted, he soon learned when they moved him from the hospital to the building that bore her name.

Alice Citrine. Even Stone knew of her.

Turning from the windows, Stone stalks across the thick cream-colored rug of his quarters. (How strange to move so confidently, without halting and probing!) He has spent the past fifteen days or so zealously practicing with his new eyes. Everything the doctor promised him is true. The miracle of sight pushed into new dimensions. It's all been thrilling. And the luxury of his situation is undeniable. Any kind of food he wants. (Although he would have been satisfied with frack---processed krill. ) Music, holovision, and most prized, the company of June. But all of a sudden today, he is feeling a little irritable. Where and what is this job they hired him for? Why has he not met his employer face to face yet? He begins to wonder if this is all some sort of ultra-elaborate sluff.

Stone stops before a full-length mirror mounted on a closet door. Mirrors still have the power to fascinate him utterly. That totally obedient duplicate imitating one's every move, will-less except for his will. And the secondary world in the background, unattainable and silent. During the years in the Bungle when he still retained his eyes, Stone never saw his reflection in anything but puddles or shards of windows. Now he confronts the immaculate stranger in the mirror, seeking clues in his features to the essential personality beneath.

Stone is short and skinny, traces of malnourishment plain in his stature. But his limbs are straight, his lean muscles hard. His skin where it shows from beneath the sleeveless black one-piece is weather-roughened and scarred. Plyoskin slippers---tough, yet almost as good as barefoot---cover his feet.

His face. All intersecting planes, like that strange picture in his bedroom. (Did June say ``Picasso''?) Sharp jaw, thin nose, blond stubble on his skull. And his eyes: faceted dull-black hemispheres: inhuman. But don't take them back, please; I'll do whatever you want.

Behind him the exit door to his suite opens. It's June. Without conscious thought, Stone's impatience spills out in words, which pile one for one atop June's simultaneous sentence, merging completely at the end.

``I want to see---''

``We're going to visit---''

``---Alice Citrine.''

Fifty floors above Stone's suite, the view of the city is even more spectacular. Stone has learned from June that the Citrine Tower stands on land that did not even exist a century ago. Pressure to expand motivated a vast landfill in the East River, south of the Brooklyn Bridge. On part of this artificial real estate, the Citrine Tower was built in the Oughts, during the boom period following the Second Constitutional Convention.

Stone boosts the photon-electron ratio of his eyes, and the East River becomes a sheet of white fire. A momentary diversion to ease his nerves.

``Stand here with me,'' June says, indicating a disk just beyond thc elevator door, a few meters from another entrance.

Stone complies. He imagines he can feel the scanning rays on him, although it is probably just the nearness of June, whose elbow touches his. Her scent fills his nostrils, and he fcrvently hopes that having eyes won't dull his other senses.

Silently the door opens for them.

June guides him through.

Alice Citrine waits inside.

The woman sits in a powered chair behind a horseshoe-shaped bank of screens. Her short hair is corn-yellow, her skin unlined, yet Stone intuits a vast age clinging to her, the same way he used to be able to sense emotions when blind. He studies her aquiline profile, familiar somehow as a face once dreamed is familiar.

She swivels, presenting her full features. June has led them to within a meter of the burnished console.

``Good to see you, Mr Stone,'' says Citrine. ``I take it you are comfortable, no complaints.''

``Yes,'' Stone says. He tries to summon up the thanks he meant to give, but can't find them anywhere, so disconcerted is he. Instead, he says tentatively, ``My job---''

``Naturally you're curious,'' Citrine says. ``It must be something underhanded or loathsome or deadly. Why else would I need to recruit someone from the Bungle? Well, let me at last satisfy you. Your job, Mr. Stone, is to study.''

Stone is dumbfounded. ``Study?''

``Yes, study. You know the meaning of the word, don't you? Or have I made a mistake? Study, learn, investigate, and whenever you feel you understand something, draft me a report.''

Stone's bafflement had passed through amazement to incredulity. ``I can't even read or write,'' he says. ``And what the frack am I supposed to study?''

``Your field of study, Mr. Stone, is this contemporary world of ours. I have had a large part, as you may know, in making this world what it is today. And as I reach the limits of my life, I grow more interested in whether what I have built is bad or good. I have plenty of reports from experts, both positive and negative. But what I want now is a fresh view from one of the underdwellers. All I ask is honesty and accuracy.

``As for reading and writing---those outmoded skills of my youth---June will assist you in learning those if you wish. But you have machines to read to you and transcribe your speech. You may start at once.''

Stone tries to assimilate this mad request. It seems capricious, a cover for deeper, darker deeds. But what can he do except say yes?

He agrees.

A tiny smile plucks at the woman's lips. ``Fine. Then our talk is over. Ch. one last thing. If you need to conduct on-site research, June must accompany you. And you will mention my sponsorship of you to no one. I don't want sycophants.''

The conditions are easy---especially having June always close---and Stone nods his acceptance.

Citrine turns her back to them then. Stone is startled by what he sees, almost believing his eyes defective.

Perched on the broad back of her chair is a small animal resembling a lemur or tarsier. Its big, luminous eyes gaze soulfully at them, its long tail arcs in a spiral above its back.

``Her pet,'' whispers June, and hurries Stone away.

\fancybreak{* * *}

The task is too huge, too complex. Stone considers himself a fool for ever having accepted.

But what else could he have done, if he wanted to keep his eyes?

Stone's cramped and circumscribed life in the Bungle has not prepared him well to fathom the multiplex, extravagant, pulsating world he has been transported to. (At least this is what he initially feels.) Literally and figuratively kept in the dark for so long, he finds the world outside the Citrine Tower a mystifying place.

There are hundreds, thousands of things he has never heard of before. People, cities, objects, events. There are areas of expertise whose names he can hardly pronounce. Areology, chaoticism, fractal modeling, paraneurology. And don't forget history, that bottomless well atop which the present moment is but a scrim of bubbles. Stone is, perhaps, most shocked by his discovery of history. He cannot recall ever having considered life as extending backward in time beyond his birth. The revelation of decades, centuries. millennia nearly pushes him into a mental abyss. How can one hope to comprehend the present without knowing all that has gone before?

Hopeless, insane, suicidal to persist.

Yet Stone persists.

He closets himself with his magic window on the world, a terminal that interfaces with the central computer in the Citrine Tower---itself a vast, unintelligible hive of activity---and through that machine to almost every other in the world. For hours on end, images and words flash by him, like knives thrown by a circus performer---knives that he, the loyal but dumb assistant, must catch to survive.

Stone's memory is excellent, trained in a cruel school, and he assimilates much. But each path he follows has a branch every few steps, and each branch splits at frequent points, and those tertiary branches also sprout new ones, no less rich than the primaries....

Once Stone nearly drowned, when a gang left him unconscious in a gutter and it began to rain. He recalls the sensation now.

June brings him three meals faithfully each day. Her presence still thrills him. Each night, as he lies abed, he replays stored images of her to lull him asleep. June bending, sitting, laughing, her Asian eyes aglow. The subtle curves of her breasts and hips. But the knowledge-fever is stronger, and he tends to ignore her as the days go by.

One afternoon Stone notices a pill on his lunch tray. He asks June its nature.

``Its a mnemotropin---promotes the encoding of long-term memories,'' she replies. ``I thought it might help you.''

Stone swallows it greedily, and returns to the droning screen.

Each day he finds a pill at lunch. His brain seems to expand to a larger volume soon after he takes them. The effect is potent, allowing him to imagine he can ingest the world. But still, each night when he finally forces himself to stop, he feels he has not done enough.

Weeks pass. He has not prepared a single sentence for Alice Citrine. What does he understand? Nothing. How can he pass judgment on the world? It's hubris, folly. How long will she wait before she kicks his ass out onto the cold street?

Stone drops his head in his hands. The mocking machine before him torments him with a steady diarrhea of useless facts.

A hand falls lightly on his quivering shoulder. Stone imbibes June's sweet scent.

Stone smashes the terminal's power stud with the base of his palm so fiercely it hurts. Blessed silenee. He looks up at June.

``I'm no damn good at this. Why'd she pick me? I don't even know where to start.''

June sits on a cushion beside him. ``Stone, I haven't said anything, because I was ordered not to direct you. But I don't think sharing a little of my experience will count as interference. You've got to limit your topic, Stone. The world's too big. Alice doesn't expect you to comprehend it all, distill it into a masterpiece of concision and sense.

``The world doesn't lend itself to such summations, anyway. I think you unconsciously know what she wants. She gave you a clue when you talked to her.''

Stone summons up that day, plays back a view he filed of the stern old woman. Her features occult June's. The visual cue drags along a phrase.

``---whether what I have built is bad or good.''

It is as if Stone's eyes have overloaded. Insight floods him with relief. Of course, the vain and powerful woman sees her life as the dominant theme of the modern era, a radiant thread passing through time, with critical nodes of action strung on it like beads. How much easier to understand a single human life than that of the whole world. (Or so he believes at the moment.) That much he thinks he can do. Chart Citrine's personal history, the ramifications of her long career, the ripples spreading from her throne. Who knows? It might indeed prove archetypal.

Stone wraps his arms around June in exultation, gives a wordless shout. She doesn't resist his embrace, and they fall back upon the couch.

Her lips are warm and complaisant under his. Her nipples seem to burn through her shirt and into his chest. His left leg is trapped between her thighs.

Suddenly he pulls back. He has seen himself too vividly: scrawny castoff from the sewer of the city, with eyes not even human.

``No,'' he says bitterly. ``You can't want me.''

``Quiet,'' she says, ``quiet.'' Her hands are on his face; she kisses his neck; his spine melts; and he falls atop her again, too hungry to stop.

``You're so foolish for someone so smart,'' she murmurs to him afterwards. ``Just like Alice.''

He does not consider her meaning.

\fancybreak{* * *}

The roof of the Citrine Tower is a landing facility for phaetons, the suborbital vehicles of companies and their executives. He feels he has learned all he can of Alice Citrine's life, while cooped up in the tower. Now he wants the heft and feel of actual places and people to judge her by.

But before they may leave, June tells Stone, they must speak to Jerrold Scarfe.

In a small departure lounge, all soft white corrugated walls and molded chairs, the three meet.

Scarfe is head of security for Citrine Technologies. A compact, wiry man, exhibiting a minimum of facial expressions, he strikes Stone as eminently competent, from the top of his permanently depilated and tattooed skull to his booted feet. On his chest he wears the CT emblem: a red spiral with an arrowhead on its outer terminus, pointing up.

June greets Scarfe with some familiarity, and asks, ``Are we cleared?''

Scarfe waggles a sheet of flimsy in the air. ``Your flight plan is quite extensive. Is it really necessary, for instance, to visit a place like Mexico City, with Mr. Stone aboard?''

Stone wonders at Scarfe's solicitude for him, an unimportant stranger. June interprets Stone's puzzled look and explains. ``Jerrold is one of the few people that know you represent Miz Citrine. Naturally, he's worried that if we run into trouble of some kind, the fallout will descend on Citrine Technologies.''

``I'm not looking for trouble, Mr. Scarfe. I just want to do my job.''

Scarfe scans Stone as intentlv as the devices outside Alice Citrine's sanctum. The favorable result is eventually expressed as a mild grunt, and the announcement, ``Your pilot's waiting. Go ahead.''

Higher off the grasping earth than he has ever been before, his right hand atop June's left knee, feeling wild and rich and free, Stone ruminates over his life of Alice Citrine, and the sense he is beginning to make of it.

Alice Citrine is 159 years old. When she was born, America was still com prised of states, rather than FEZ and ARCadias. Man had barely begun to fly. When she was in her sixties, she headed a firm called Citrine Biotics. This was the time of the Trade Wars, wars as deadly and decisive as military ones, yet fought with tarriffs and five-year plans, automated assembly lines and fifth-generation decisionmaking constructs. This was also the time of the Second Constitutional Convention, that revamping of America for the state of war.

During the years when the country was being divided into Free Enterprise Zones---urban, hi-tek, autonomous regions, where the only laws were those imposed by corporations and the only goal was profits and dominance---and Areas of Restrictive Control---rural, mainly agricultural enclaves, where older values were strictly enforced---Citrine Biotics refined and perfected the work of their reseachers and others in the field of carbon chips: microbiological assemblies, blood-borne programmed repair units. The final product, marketed by Citrine to those who could afford it, was near-total rejuvenation, the cell-slough---or, simply, the sluff.

Citrine Biotics headed the Fortune 500 within six years.

By then it was Citrine Technologies.

And Alice Citrince sat atop it all.

But not forever.

Entropy will not be cheated. The information-degradation that DNA undergoes with age is not totally reversible. Errors accumulate despite the hardworking carbon chips. The body dutiful gives out the end.

Alice Citrine is nearing the theoretical close of her extended life. Despite her youthful looks, one day a vital organ will fail, the result of a million bad transcriptions.

She needs Stone, of all people, to justify her existence.

Stone squeezes June's knee and relishes the sense of importance. For the first time in his sad and dingy life, he can make a difference. His words, his perceptions matter. He is determined to do a good job, to tell the truth as he perceives it.

``June,'' Stone says emphatically, ``I have to see everything.''

She smiles. ``You will, Stone. You will indeed.''

\fancybreak{* * *}

And the phaeton comes down---in Mexico City, which crashed last year at population 35 million. Citrine Technologies is funding a relief effort there, operating out of their Houston and Dallas locations. Stone is suspicious of the motives behind the campaign. Why didn't they step in before the point of collapse? Can it be that they are worried now only about refugees flooding across the border? Whatever the reasons, though, Stone cannot deny that the CT workers are a force for good, ministering to the sick and hungry, reestablishing electrical power and communications, propping up (acting as?) the city government. He boards the phaeton with his head spinning, and soon fmds himself---in the Antarctic, where he and June are choppered out from the CT domes to a krill-processing ship, source of so much of the world's protein. June finds the frack stench offensive, but Stone breathes deeply, exhilarated at being afloat in these strange and icy latitudes, watching the capable men and woman work. June is happy to be soon aloft, and then---in Peking, where CT heuristic specialists are working on the first Artificial Organic Intelligence. Stone listens with amusement to a debate over whether the AOI should be named K'ung Fu-tzu or Mao.

The week is a kaleidoscopic whirl of impressions. Stone feels like a sponge, soaking up the sights and sounds so long denied him. At one point he finds himself leaving a restaurant with June, in a city whose name he has forgotten. In his hand is his ID card, with which he had just paid for their meal. A holoportrait stares up from his palm. The face is cadaverous, filthy, with two empty, crusted sockets for eyes. Stone remembers the warm laser fingers taking his holo in the Immigration Office. Was that really he? The day seems like an event from someone else's life. He pockets his card, unsure whether to have the holo updated or to keep it as a token of where he has come from.

And where he might end up?

(What will she do with him after he reports?)

When Stone asks one day to see orbital installations, June calls a halt. ``I think we've done enough for one trip, Stone. Let's get back, so you can start to put it all together.''

With her words, a deep boneweariness suddenly overtakes Stone, and his manic high evaporates. He silently assents.

\fancybreak{* * *}

Stone's bedroom is dark, except for the diffuse lights of the city seeping in through a window. Stone has multiplied his vision, the better to admire the naked glowing form of June beside him. He has found that colors grow muddy in the absence of enough photons, but that a very vivid black-and white image can be had. He feels like a dweller in the past century, watching a primitive film. Except that June is very much alive beneath his hands.

June's body is a tracery of lambent lines, like some arcane capillary circuitry in the core of Mao/K'ung Futzu. Following the current craze, she has had a subdermal pattern of microchannels implanted. The channels are filled with synthetic luciferase, the biochemical responsible for the glow of fireflies, which she can now trigger at will. In the afterglow of their lovemaking, she has set herself alight. Her breasts are whorls of cold fire, her shaven pubic mound a spiral galaxy dragging Stone's gaze into illimitable depths.

June is speaking in a abstracted way of her life before Stone, pondering the ceiling while he idly strokes her.

``My mother was the only surviving child of two refugees. Vietnamese. Came to America shortly after the Asian War. Did the only thing they knew how to do, which was fish. They lived in Texas, on the Gulf. My mother went to college on a scholarship. There she met my father, who was another refugee of sorts. He left Germany with his parents after its Reunification. They said the compromise government was neither one thing nor the other, and they couldn't deal with it. I guess my background is some sort of microcosm of a lot of the upheavals of our times.''

She catches Stone's hand between her knees and holds it tightly. ``But I feel a calmness with you right now, Stone.''

As she continues to speak of things she has seen, people she has known, her career as Citrine's personal assistant, the oddest feeling creeps over Stone. As her words integrate themselves into his growing picture of the world, he feels the same abyssmal tidal suck that he first felt upon learning of history.

Before he can decide consciously if he even wants to know or not, he finds himself saying, ``June. How old are you?''

She falls silent. Stone watches her staring blindly at him, unequipped with his damned perceptive eyes.

``Over sixty,'' she finally says. ``Does it matter?''

Stone finds he cannot answer, does not know if her age does matter or not.

Slowly June wills her glowing body dark.

\fancybreak{* * *}

Stone bitterly amuses himself with what he likes to think of as his art.

Perusing the literature on the silicon chip that dwells in his skull, he found that it has one property not mentioned by the doctor. The contents of its RAM can be squirted in a signal to a stand-alone computer. There the images he has collected may be displayed for all to see. What is more, the digitized images may be manipulated, recombined with themselves or with stock graphics, to form entirely lifelike pictures of things that never existed. These, of course, may be printed off.

In effect, Stone is a living camera and his computer a complete studio.

Stone has been working on a series of images of June. The color printouts litter his quarters, hung on wall and underfoot.

June's head on the Sphinx's body. June as La Belle Dame Sans Merci. June's face imposed upon the full moon, Stone asleep in a field as Endymion.

The portraits are more disturbing than soothing, and, Stone senses, quite unfair. But Stone feels that he is gaining some therapeutic effect from them, that each day he is inching closer to his true feelings for June.

He still has not spoken to Alice Citrine. That nags him greatly. When will he deliver his report? What will he say?

The problem of when is solved for him that afternoon. Returning from one of the tower's private gyms, he finds his terminal flashing a message.

Citrine will see him in the morning.

\fancybreak{* * *}

Alone this second time, Stone stands on the plate before Alice Citrine's room, allowing his identity to be verified. He hopes the results will be shared with him when the machine finishes, for he has no idea of who he is.

The door slides into the wall, a beckoning cavern mouth.

Avernus, Stone thinks, and enters.

Alice Citrine remains where she sat so many event-congested weeks ago, unchanged, seemingly sempiternal. The screens flicker in epileptic patterns on three sides of her instrumented chair. Now, however, she ignores them, her eyes on Stone, who advances with trepidation.

Stone stops before her, the console an uncrossable moat between them. He notes her features this second time with a mix of disbelief and alarm. They seem to resemble his newly fleshed-out face to an uncanny degree. Has he come to look like this woman simply by working for her? Or does life outside the Bungle stamp the same harsh lines on everyone?

Citrine brushes her hand above her lap, and Stone notices her pet curled in the valley of her brown robe, its preternaturally large eyes catching the colors on the monitors.

``Time for a preliminary report, Mr. Stone,'' she says. ``But your pulse rate is much too high. Relax a bit---everything does not hinge on this one session.''

Stone wishes he could. But there is no offer of a seat, and he knows that what he says will be judged.

``So---what do you feel about this world of ours, which bears the impress of myself and others like me?''

The smug superiority in Citrine's voice drives all caution from Stone's thoughts, and he nearly shouts, ``It's unfair.'' He pauses a moment, and then honesty forces him to admit, ``Beautiful, gaudy, exciting at times---but basically unfair.''

Citrine seems pleased at his outburst. ``Very good, Mr. Stone. You have discovered the basic contradiction of life. There are jewels in the dung heap, tears amid the laughter, and how it is all parceled out, no one knows. I'm afraid I cannot shoulder the blame for the world's unfairness, though. It was unfair when I was a child, and remained unfair despite all my actions. In fact, I may have increased the disparity a little. The rich are richer, the poor seemingly poorer by comparison. But still, even the titans are brought down by death in the end.''

``But why don't you try harder to change things?'' Stone demands. ``It has to be within your power ``

For the first time, Citrine laughs, and Stone hears an echo of his own sometimes bitter caw ``Mr. Stone, `` she says, ``I have all I can do to stay alive. And I do not mean taking care of my body---that is attended to automatically. No, I mean avoiding assassination. Haven't you gleaned the true nature of business in this world of ours?''

Stone fails to see her meaning, and says so.

``Allow me to brief you, then. It might alter a few of your perceptions. You are aware of the intended purpose of the Second Constitutional Convention, are you not? It was couched in high-flown phrases like ‘unleash the strength of the American system,' and ‘meet foreign competition head-to-head, ensuring a victory for American business that will pave the way for democracy throughout the world.' All very noble-sounding. But the actual outcome was quite different. Business has no stake in any political system per se. Business cooperates to the extent that cooperation furthers its own interests. And the primary interest of business is growth and dominance. Once the establishment of the Free Enterprise Zones freed corporations from all constraints, they reverted to a primal struggle, which continues to this day.''

Stone attempts to digest all this. He has seen no overt struggles on his journey. Yet he has vaguely sensed undercurrents of tension everywhere. But surely she is overstating the case. Why, she makes the civilized world sound no more than a large-scale version of the anarchy of the Bungle.

As if reading his mind, Citrine says, ``Did you ever wonder why the Bungle remains blighted and exploited in the midst of the city, Mr. Stone, its people in misery?''

Suddenly all of Citrine's screens flash with scenes of Bungle life, obedient to her unvoiced command. Stone is taken aback. Here are the sordid details of his youth: urinereeking alleys with rag-covered forms lying halfway between sleep and death, the chaos around the Immigration Office, the razor-topped fence by the river.

``The Bungle,'' Citrine continues, ``is contested ground. It has been so for over eighty years. The corporations cannot agree over who is to develop it. Any improvement made by one is immediately destroyed by the tactical team of another. This is the kind stalemate prevalent in much of the world.

``Everyone wanted to be pulled into an earthly paradise by his purse strings, like a Krishna devotee by his pigtail. But this patchwork of fiefdoms is what we got instead.''

Stone's conceptions are reeling. He came expecting to be quizzed and to disgorge all he thought he knew. Instead, he has been lectured and provoked, almost as if Citrine is testing whether he is a partner fit to debate. Has he passed or failed?

Citrine settles the question with her next words. ``That's enough for today, Mr. Stone. Go back and think some more. We'll talk again.''

\fancybreak{* * *}

For three weeks Stone meets nearly every day with Citrine. Together they explore a bewildering array of her concerns. Stone gradually becomes more confident of himself, expressing his opinions and observations in a firmer tone. They do not always mesh with Citrine's, yet on the whole he feels a surprising kinship and affinity with the ancient woman.

Sometimes it almost seems as if she is grooming him, master and apprentice, and is proud of his progress. At other times she holds herself distant and aloof.

The weeks have brought other changes. Although Stone has not slept with June since that fateful night, he no longer sees her as the siren figure of his portraits, and has stopped depicting her in that fashion. They are friends, and Stone visits with her often, enjoys her company, is forever grateful to her for her part in rescuing him from the Bungle.

During his interviews with Citrine, her pet is a constant spectator. Its enigmatic presence disturbs Stone. He has found no trace of sentimental affection in Citrine, and cannot fathom her attention to the creature.

One day Stone finally asks Citrine outright why she keeps it.

Her lips twitch in what passes for her smile. ``Aegypt is my touchstone on the true perspective of things, Mr. Stone. Perhaps you do not recognize her breed.''

Stone admits ignorance.

``This is Aegyptopithecus zeuxis, Mr. Stone. Her kind last flourished several million years ago. Currently she is the only specimen extant, a clone---or rather, a recreation based on dead fossil cells.

``She is your ancestor and mine, Mr. Stone. Before the hominids, she was the representative of mankind on earth. When I pet her, I contemplate how little we have advanced.''

Stone turns and stalks off, unaccountably repelled by the antiquity of the beast and the insight into her mistress.

This is the last time he will see Alice Citrine.

\fancybreak{* * *}

Night time.

Stone lies alone in bed, replaying snapshots of his terminal screen, of pre-FEZ history that has eluded him.

History that has eluded him.

Suddenly there is a loud crack like the simultaneous discharge of a thousand gigantic arcs of static electricity. At that exact second, two things happen: Stone feels an instant of vertigo.

His eyes go dead.

Atop these shocks, an enormous explosion above his head rocks the entire shaft of the Citrine Tower.

Stone shoots to his feet, clad only in briefs, barefoot as in the Bungle. He can't believe he's blind. But he is. Back in the dark world of smell and sound and touch alone.

Alarms are going off everywhere. Stone rushes out into his front room with its useless view of the city. He approaches the front door, but it fails to open. He reaches for the manual control, but hesitates.

What can he do while blind? He'd just stumble around, get in the way. Better to stay here and wait out whatever is happening.

Stone thinks of.June then, can almost smell her perfume. Surely she will be down momentarily to tell him what's going on. That's it. He'll wait for June.

Stone paces nervously for three minutes. He can't believe his loss of vision. Yet somehow he's always known it would happen.

The alarms have stopped, allowing Stone to hear near-subliminal footsteps in the hall, advancing on his door. June at last? No, everything's wrong. Stone's sense-of-life denies that the visitor is anyone he knows.

Stone's Bungle instincts take over. He ceases to speculate about what is happening, is all speed and fear.

The curtains in the room are tied back with thin but strong velvet cords. Stone rips one hastily down, takes up a position to the side of the outer door.

The shock wave when the door is hit nearly knocks Stone down. But he regains his balance, tasting blood, just as the man barrels in and past him.

Stone is on the man's burly back in a flash, legs wrapped around his waist, cord around his throat.

The man drops his gun, hurls himself back against the wall. Stone feels ribs give, but he tightens the rope, muscles straining.

The two stagger around the room, smashing furniture and vases, locked in something like an obscene mating posture.

Eventually, after forever, the man keels over, landing heavily atop Stone.

Stone never relents, until he is sure the man has stopped breathing.

His attacker is dead.

Stone lives.

He wriggles painfully out from under the slack mass, shaken and hurt.

As he gets his feet under him, he hears more people approaching, speaking.

Jerrold Scarfe is the first to enter, calling Stone by name. When he spots Stone, Scarfe shouts, ``Get that stretcher over here.''

Men bundle Stone onto the canvas and begin to carry him off.

Scarfe walks beside him, and conducts a surrealistic converstion.

``They learned who you were, Mr. Stone. That one fracking bastard got by us. We contained the rest in the wreckage of the upper floors. They hit us with a directed electromagnetic pulse that took out all our electronics, including your vision. You might have lost a few brain cells when it burned, but nothing that can't be fixed. After the EMP, they used a missile on Miz Citrine's floor. I'm afraid she died instantly.''

Stone feels as if he is being shaken to pieces, both physically and mentally. Why is Scarfe telling him this? And what about June?

Stone croaks her name.

``She's dead, Mr. Stone. When the raiders assigned to bag her had begun to work on her, she killed herself with an implanted toxin-sac.''

All the lilies wither when winter draws near.

The stretcher party has reached the medical facilities. Stone is lifted onto a bed, and clean hands begin to attend to his injuries.

``Mr. Stone, `` Scarfe continues, ``I must insist that you listen to this. It's imperative, and it will take only a minute. ``

Stone has begun to hate this insistent voice. But he cannot close his ears or lapse into blessed unconsciousness, so he is forced to hear the cassette Scarfe plays.

It is Alice Citrine speaking.

``Blood of my blood,'' she begins, ``closer than a son to me. You are the only one I could ever trust.''

Disgust washes over Stone as everything clicks into place and he realizes what he is.

``You are hearing this after my death. This means that what I have built is now yours. All the people have been bought to ensure this. It is now up to you to retain their loyalty. I hope our talks have helped you. If not, you will need even more luck than I wish you now.

``Please forgive your abandonment in the Bungle. It's just that a good education is so important, and I believe you received the best. I was always watching you.''

Scarfe shuts off the cassette. ``What are your orders, Mr. Stone?''

Stone thinks with agonizing slowness while unseen people minister to him.

``Just clean this mess up, Scarfe. Just clean up this whole goddamn mess.''

But he knows as he speaks that this is not Scarfe's job.

It's his.